ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-24 notebooks/moons.qmd

```{julia}
# Model parameters:
epochs = 500
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden,), 
    σ=activation
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                      # finaliser function
```

>>>>

```{julia}
# Model parameters:
epochs = 500
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden,), 
    σ=activation
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                      # finalizer function
```

### 2023-09-24 paper/tables.Rmd

```{r}
res_path <- "results/"
files <- list.files(res_path)
dt <- lapply(files[grepl("_benchmark.csv", files)], function(x) {
    fread(file.path(res_path, x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt[,ce:=NULL]
synth <- c("Moons", "Circles", "Linearly Separable")
dt[,source:=ifelse(dataname %in% synth, "synthetic", "real-world")]
reported_data <- c(
  "MNIST",
  "GMSC",
  "Linearly Separable",
  "Moons",
  "Circles"
)
dt <- dt[dataname %in% reported_data]
dt[,non_valid:=variable=="validity" & value==0.0,.(sample,dataname,generator,model,target,factual,source)]
dt[,non_valid:=any(non_valid==TRUE),.(sample,dataname,generator,model,target,factual,source)]
dt_valid <- dt[non_valid==FALSE]
```

>>>>

```{r}
res_path <- "results/"
files <- list.files(res_path)
dt <- lapply(files[grepl("_bmk.csv", files)], function(x) {
    fread(file.path(res_path, x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt[,ce:=NULL]
synth <- c("Moons", "Circles", "Linearly Separable")
tabular <- c("GMSC", "German Credit", "California Housing")
dt[,source:=ifelse(dataname %in% synth, "synthetic", ifelse(dataname %in% tabular, "tabular", "vision"))]
dt[,non_valid:=variable=="validity" & value==0.0,.(sample,dataname,generator,model,target,factual,source)]
dt[,non_valid:=any(non_valid==TRUE),.(sample,dataname,generator,model,target,factual,source)]
dt_valid <- dt[non_valid==FALSE]
```
